\label{sec:use-case}
\begin{itemize}
	 \item \textbf{Anti-lock Braking system and Traction Control Systems:} ABS components include: a wheel- speed sensor, a hydraulic modulator and an Electronic Control Unit (ECU) for signal processing and control and triggering of the signal lamp and of the actuators in the hydraulic modulator.
	 If any of these components malfunction and the user is not notified in time to take corrective steps, there can be grave danger to the driver’s, passengers’ and pedestrians’ lives.
	 
	 \item \textbf{Airbags:} There are a number of other reasons that may cause the airbags to fail.
	 \begin{enumerate}
	 	\item \textbf{Airbag backup battery} has already been depleted- Check for it have a threshold voltage that battery must have, and notify to users immediately.
	 	\item \textbf{Faulty Sensors:} Sensors may malfunction or be inadvertently tripped, which might fail to deploy during actual crash.
	 	\item \textbf{Soaked Airbag Module:} If your vehicle has been touched by water damage (maybe have a sensor to get the moisture level if it is regularly exposed and increasing moisture/water particles.
	 	\item \textbf{Damaged Airbag Clock Spring:} he airbag clock spring is there for the continuity between the electrical wiring of your vehicle and your driver-side airbag. The rotary electrical connector allows the steering wheel to turn while keeping a connection between the wheel’s airbag, horn, and the electrical system. So, if the clock spring isn’t working, then the airbag won’t deploy. The clock spring will coil in and out with every turn of your steering wheel so it is only normal that it will become worn out over time. The poor connection will give way for potential airbag failures 
	 \end{enumerate}
	 
	 \item \textbf{Seat belt system switch sensors:} Seat belts plays major role in safety for effective working of airbags.
	 
	 \item \textbf{Autonomous Emergency braking system }is a crucial part of the autonomous car. It one of the standard safety equipment of a self-driving car. This AEB works by scanning the distance of the road measuring the distance of the front road. And everything is controlled here by using sensors like ultrasonic sensors etc. If these sensors don’t work properly collision may occur. So, one of the approaches of our system to diagnose whether these sensors work properly, if not it will notify the user for maintenance.
	 
	 \item In Germany autobahn, the minimum seed of driving is 130kmph. People usually drives their car at speed of 150-225 kmph. As we also know that entry and exit from autobahn is not possible from everywhere. If one of the cars runs out of fuel in the middle of autobahn, then there is nowhere to stop in the middle because if it is stopped then it will be a huge catastrophic, involving many cars and may cause a huge risk to human life. So, it is very important to check the fuel level so that the car does not stop in the middle of the autobahn, and it will safely exit from there and go to the nearest fuel station. That is why our system will monitor the fuel level in the running car and if the decreases to less than 5 percentage it will immediately notify user. And as it is an autonomous car means automatic driving to destination, and in this scenario, destination will have one more mid stop for fueling station.
	 
	 \item \textbf{Trouble code analysis:} Finding bugs in code that can lead to vehicle failures.
	 \item \textbf{Roadside assistance:} Vehicle data helps roadside service providers determine where exactly the car broke down and what’s wrong with it. It also helps determine if roadside assistance is even needed: maybe over-the-phone assistance about how to fix the car would be enough. Tracking vehicle health indicators: an early warning that a part is likely to fail and the estimated time to failure.

\end{itemize}